```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
library(knitr)
opts_knit$set(base.dir='./')
opts_chunk$set(prompt=TRUE, comment='', fig.path='figures/')
```

```{r,results='hide',echo=FALSE}
library(capm)
psu.ssu <- read.csv(file = 'psu.ssu.csv')
set.seed(4)
pilot.psu <- SamplePPS(psu.ssu = psu.ssu,
                       psu = 10,
                       write = FALSE)
set.seed(4)
pilot.ssu <- SampleSystematic(
   psu.ssu = pilot.psu,
    su = 5, write = FALSE)
final.psu <- SamplePPS(psu.ssu, 20, write = F)
final.ssu <- SampleSystematic(final.psu, 15, write = F)
```

Having defined the final sample, suppose we went to visit all the selected households and the collected data were recorded in a file called `survey.data.csv`.  (to see a description of each variable, see the help page of the file typing `?survey.data`).

```{r}
survey.data <- read.csv('survey.data.csv')
head(survey.data)
```

To estimate the population parameters, the first step is to define the sampling design from which the data came from. To do this, we need a file containing all the sampling units in the population (`psu.ssu`) and a file with the sampling data (`survey.data`). In this last file, the columns containing PSU's and SSU's identifiers must be specified, as well as the number of PSU's included in the sample (if a PSU was selected more than once, each occurrence must be counted).

```{r}
design <- DesignSurvey(sample = survey.data,
                       psu.ssu = psu.ssu,
                       psu.col = 2,
                       ssu.col = 1,
                       psu.2cd = 20)
```

Setting the type of estimate for each variable is easy. Empty quotes exclude a variable from the estimation procedure.

```{r}
variables <- c('total', 'prop', 'mean', 'prop',
               'prop', 'total', rep('prop', 8))
```

It is convenient to confirm that we have defined the type of estimates we want.

```{r}
cbind(names(design$variables), variables)
```

Now we are ready to get our first estimates.

```{r}
(estimates <- SummarySurvey(design = design,
                            variables = variables,
                            rnd = 3))
```

The previous output is very useful but might not be enough. Let's make a copy (`sample1`) of a transformed subset of `survey.data`, to estimate the total number of sterilized animals (instead of the proportion) and to get estimates conditioned on sex.

```{r}
sample1 <-
    survey.data[, c('interview_id', 'psu',
                    'dogs', 'sex', 'sterilized',
                    'sterilized.ly', 'fate')]
sample1[, 'sterilized'] <-
    as.character(sample1[, 'sterilized'])
sample1[which(sample1$sterilized == 'yes'),
        'sterilized'] <- 1
sample1[which(sample1[, 'sterilized'] == 'no'),
        'sterilized'] <- 0
sample1[, 'sterilized'] <-
    as.numeric(sample1[, 'sterilized'])
```

After defining a sampling design in the usual way

```{r}
design.sex <- DesignSurvey(sample = sample1,
                           psu.ssu = psu.ssu,
                           psu.col = 2,
                           ssu.col = 1,
                           psu.2cd = 20)
```

we can create a design for each sex.

```{r}
design.f <- subset(design.sex, sex == 'Female')
design.m <- subset(design.sex, sex == 'Male')
```

From here, there is nothing new.

```{r}
names(design.sex$variables)
variables.sex <- c('total', '', 'total', 
                   'prop', 'prop')
cbind(names(design.sex$variables),
      variables.sex)
(estimates.f <- SummarySurvey(design.f,
                              variables.sex,
                              rnd = 3))
(estimates.m <- SummarySurvey(design.m,
                              variables.sex,
                              rnd = 3))
```

